The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-12-05 paper/ms.tex
jofre changes
changes

% Abstract of the paper
\begin{abstract}
We present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained in the \kepler four-year mission to reconstruct light curves of 102~stars too bright to have been otherwise targeted. We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission. In this paper, we focus on 66~red giants for which we detect solar-like oscillations, characterizing 34 of these in detail with spectroscopic chemical abundances and asteroseismic masses as benchmark stars. We also classify the whole sample, finding nearly all to be variable, with classical pulsations and binary effects. All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
\end{abstract}

@@

% Beyond searching for planets, 
\kepler has revolutionized the field of asteroseismology for solar-like oscillations \citep{2010PASP..122..131G,2010ApJ...713L.169C}. It has yielded the detection of gravity-mode period spacings for red giants \citep{rggmodes,2014A&A...572L...5M}, enabling probes of interior rotation \citep{rggmoderotation,2012A&A...548A..10M,2012ApJ...756...19D} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium,2012A&A...540A.143M}. It has also permitted the determination of ages and fundamental parameters of cool main-sequence stars \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages,2016MNRAS.456.2183D,2018MNRAS.479.4786V}. %revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}. %By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading~\citet{vansadersgyro}~to suggest a qualitative change in dynamo mechanism as stars age through the main-sequence.

@@

In the case of HD~181878, a red giant, there is clear and significant contamination from an M~giant, as is seen in Figure~\ref{contamination}. Likewise HD~183383 shows two different stars, depending on the quarter: some parts are likely from an ellipsoidal variable with a period of 6.46 days, other parts are from an RR Lyrae pulsator. Between seasons, there is an extra hump of power near the red giant oscillations in HD~175740; extra low frequency power in HD~180658; one coherent peak in  HD~182694; high frequency contamination in HD~181597 possibly from an EB; and a very significant difference in amplitude between seasons for BD~+39~3882. In other cases visual inspection does not show severe contamination, but in all cases we recommend that users of these light curves carefully check for differences between odd and even quarters.

@@

\caption{\label{contamination}
Power spectra of odd and even quarters of HD~181778. It is clear from inspection that while odd quarters have the power spectrum expected of a giant star, even quarters have very high amplitude coherent oscillations typical of an M~giant.}
\end{figure}

@@

Among the~66 red giants identified in this sample, for~32 the timescale of their variability is similar to the length of a \kepler quarter and they are thus badly affected by systematics and systematics correction. In Table~\ref{all_stars} we have noted these as `long-period variables' (LPVs). For the~34 giants for with high-SNR shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}. These constrain fundamental stellar parameters through the approximate scaling relations:

@@

We have obtained high-resolution spectroscopy with TRES for~63 stars, mainly giants, in order to constrain stellar parameters and elemental abundances. Operating with spectral resolving power $R=44 000$, we have obtained spectra with a mean signal-to-noise ratio (SNRs) of $\sim 100$  per resolution element. Although this resolution and SNR are sufficient for an exploratory study, a more detailed analysis will require APOGEE or a similar instrument to obtain greater spectral coverage. From this observing run we have~33 unique targets with seismic \logg and spectra, comparable to the 36 of the \gaia benchmark set \citep{2018RNAAS...2c.152J} and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations. %Due to observing constraints, we were unable to obtain spectra for BD+42~3150, BD+48~2904, HD~176209, HD~182354, HD~189636AB, or HD~189750. % figure out this discrepancy?

@@

Individual elemental abundances were derived by first fixing the stellar atmospheric parameters to those determined above. Spectra were then synthesized in regions centered around an absorption feature of the element in question with different [X/Fe] values. A $\chi^2$ minimization procedure was then done to derive the best fitting abundance for each line. The reported abundances are the median [X/Fe] value of the various line regions for each element. Abundance uncertainties reported are the standard error in the line-by-line abundance ratios. Where only one line exists for a given element, we conservatively assumed the standard error is 0.10~dex. In principle, these uncertainties are underestimated because there they do not include the errors driven by imperfect stellar parameters and other systematic errors arising, for instance, from incorrect line list data. We do note, however, thus use of asteroseismology greatly reduces the uncertainties caused by the stellar parameters \citep[see][for a longer discussion on this]{hawkinsapogee}.

To achieve the most precise abundances we have derived them both with and without a line-by-line differential approach with respect to Arcturus ($\alpha$~Bo\"{o}tis), using the method described by \citet{hawkinsapogee} and the Arcturus abundances from \citep{gaiabenchmark4}. Choosing this method means we do not derive the abundances for neutron capture  elements (e.g. Sr, Y, Zr, Ba, La, Nd, Eu) in a differential way because there are no estimated values for these elements at the appropriate benchmark parameters of Arcturus. For these elements we instead derived the chemical abundances in an absolute way, where the solar abundances of \cite{Asplund2005} were assumed. The uncertainty in the abundances are taken as the line-by-line dispersion, or assumed to be 0.10 when just one line is available. No abundances for oxygen could be reliably derived for any of the stars in our spectroscopic sample by either method.

@@

We determined the mass, radius, and age for the 33 red giants from their atmospheric and asteroseismic observables (see Table ) using the BAyesian STellar Algorithm \citep[\textsc{basta}][]{silvaaguirre2015,silvaaguirre2017}. \textsc{basta} compares the observed properties with predictions from theoretical models of stellar evolution, in this case the recently updated BaSTI (a Bag of Stellar Tracks and Isochrones) stellar models and isochrones library \citep{Hidalgo:2018dy} with overshooting and no mass-loss.

@@

\caption{\label{alphael}
The [Mg/Fe], [Si/Fe], [Ti/Fe], [V/Fe] (left panel) and [Al/Fe], [Ca/Fe], [Ni/Fe], [Cr/Fe] (right panel) abundance ratios as a function of iron for our stars (black circles). We also show a representative sample of Galactic disk stars from \citet[open red square,][]{Bensby2014}, \citet[open orange squares,][]{Adibekyan2012}, \citet[light green circles][]{Battistini2015}. These elemental ratios show that the chemical composition of our sample is consistent with the Galactic disk population. } %Mg was chosen as an illustrative $\alpha$-element. } 
\end{figure*}

>>>>

% Abstract of the paper
\begin{abstract}
We present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained in the \kepler four-year mission to reconstruct light curves of 102~stars too bright to have been otherwise targeted. We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission. In this paper, aside from publishing the light curves of these stars, we focus on 66~red giants for which we detect solar-like oscillations, characterizing 34 of these in detail with spectroscopic chemical abundances and asteroseismic masses as benchmark stars. We also classify the whole sample, finding nearly all to be variable, with classical pulsations and binary effects. All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
\end{abstract}

@@

% Beyond searching for planets, 
\kepler has revolutionized the field of asteroseismology both for solar-like oscillations \citep{2010PASP..122..131G,2010ApJ...713L.169C} and for coherent heat-engine driven oscillations \citep{2018arXiv180907779A}. It has yielded the detection of gravity-dominated mixed mode period spacings for red giants \citep{rggmodes,2014A&A...572L...5M}, enabling probes of interior rotation \citep{rggmoderotation,2012A&A...548A..10M,2012ApJ...756...19D} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium,2012A&A...540A.143M}. It has also permitted the determination of ages and fundamental parameters of cool main-sequence stars \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages,2016MNRAS.456.2183D,2018MNRAS.479.4786V}. \kepler gravity-mode asteroseismology has also been used to derive the internal rotation profiles of intermediate mass stars \citep{2015ApJ...810...16T,2018A&A...618A..24V}. %revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}. %By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading~\citet{vansadersgyro}~to suggest a qualitative change in dynamo mechanism as stars age through the main-sequence.

@@

In the case of HD~181878, a red giant, there is clear and significant contamination from a star with several low-frequency pulsations, as is seen in Figure~\ref{contamination}. Likewise HD~183383 shows two different stars, depending on the quarter: some parts are likely from an ellipsoidal variable with a period of 6.46 days, other parts are from an RR Lyrae pulsator. Between seasons, there is an extra hump of power near the red giant oscillations in HD~175740; extra low frequency power in HD~180658; one coherent peak in  HD~182694; high frequency contamination in HD~181597 possibly from an EB; and a very significant difference in amplitude between seasons for BD~+39~3882. In other cases visual inspection does not show severe contamination, but in all cases we recommend that users of these light curves carefully check for differences between odd and even quarters.

@@

\caption{\label{contamination}
Power spectra of odd and even quarters of HD~181778. It is clear from inspection that while odd quarters have the power spectrum expected of a giant star, even quarters have very high amplitude coherent oscillations.}
\end{figure}

@@

Among the~66 red giants identified in this sample, for~32 the timescale of their variability is similar to the length of a \kepler quarter and they are thus badly affected by systematics which are hard to correct with the CBV approah. In Table~\ref{all_stars} we have noted these as `long-period variables' (LPVs). For the~34 giants for with high-SNR shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}. These constrain fundamental stellar parameters through the approximate scaling relations:

@@

We have obtained high-resolution spectroscopy with TRES for~63 stars, mainly giants, in order to constrain stellar parameters and elemental abundances. Operating with spectral resolving power $R=44 000$, we have obtained spectra with a mean signal-to-noise ratio (SNRs) of $\sim 100$  per resolution element. %Although this resolution and SNR are sufficient for an exploratory study, a more detailed analysis will require APOGEE or a similar instrument to obtain greater spectral coverage. 
From this observing run we have~33 unique targets with seismic \logg and spectra, comparable to the 36 of the \gaia benchmark set \citep{2018RNAAS...2c.152J} and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations. %Due to observing constraints, we were unable to obtain spectra for BD+42~3150, BD+48~2904, HD~176209, HD~182354, HD~189636AB, or HD~189750. % figure out this discrepancy?

@@

Individual elemental abundances were derived by first fixing the stellar atmospheric parameters to those determined above. Spectra were then synthesized in regions centered around an absorption feature of the element in question with different [X/Fe] values. A $\chi^2$ minimization procedure was then done to derive the best fitting abundance for each line. The reported abundances are the median [X/Fe] value of the various line regions for each element. Abundance uncertainties reported are the standard error in the line-by-line abundance ratios. Where only one line exists for a given element, we assumed the standard error to be 0.10~dex. In principle, these uncertainties are underestimated because there they do not include the errors driven by imperfect stellar parameters and other systematic errors arising, for instance, from incorrect line list data. We do note, however, the use of asteroseismology to determine \logg greatly reduces the uncertainties caused by the stellar parameters \citep[see][for a longer discussion on this]{hawkinsapogee}.

To achieve the most precise abundances we have derived them both with and without a line-by-line differential approach with respect to Arcturus ($\alpha$~Bo\"{o}tis), using the method described by \citet{hawkinsapogee} and the Arcturus abundances from \citet{gaiabenchmark4}. Choosing this method means we do not derive the abundances for neutron capture  elements (e.g. Sr, Y, Zr, Ba, La, Nd, Eu) in a differential way because there are no estimated values for these elements at the appropriate benchmark parameters of Arcturus. For these elements we instead derived the chemical abundances in an absolute way, where the solar abundances of \cite{Asplund2005} were assumed. The uncertainty in the abundances are either the line-by-line dispersion, or assumed to be 0.10 when just one line is available. No abundances for oxygen could be reliably derived for any of the stars in our spectroscopic sample by either method.

@@

We determined the mass, radius, and age for the 33 red giants from their atmospheric and asteroseismic observables (see Table~\ref{astero_table}) using the BAyesian STellar Algorithm \citep[\textsc{basta}][]{silvaaguirre2015,silvaaguirre2017}. \textsc{basta} compares the observed properties with predictions from theoretical models of stellar evolution, in this case the recently updated BaSTI (a Bag of Stellar Tracks and Isochrones) stellar models and isochrones library \citep{Hidalgo:2018dy} with overshooting and no mass-loss.

@@

\caption{\label{alphael}
The [Mg/Fe], [Si/Fe], [Ti/Fe], [V/Fe] (left panel) and [Al/Fe], [Ca/Fe], [Ni/Fe], [Cr/Fe] (right panel) abundance ratios as a function of iron for our stars (black circles). We also show a representative sample of Galactic disk stars from \citet[open red squares]{Bensby2014}, \citet[open orange squares]{Adibekyan2012}, and \citet[light green circles]{Battistini2015}. These elemental ratios show that the chemical composition of our sample is consistent with the Galactic disk population. } %Mg was chosen as an illustrative $\alpha$-element. } 
\end{figure*}
